Numerical Solution of Point Defect Equations by MOOSE

### 2021-01-01 examples/point_defects/article/article.tex
article-edit

@@

  The results of bencmark problem, previously discussed in Fig. \ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations. Table \ref{table:sink_strengths_calculations} show the comparison of calculations.
    \begin{table}[h!]
      \centering
      \caption{Comparison of sink strength calculations}
      \label{table:sink_strengths_calculations}
      \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}||  }
         \hline
          & MOOSE & Analytical\\
         \hline\hline\hline
         ${Z_{gb,i}}$  & 1.257206e-05 m & 1.257332e-05 m\\
         ${Z_{gb,v}}$  & 1.256941e-05 m & 1.257332e-05 m\\
         ${k_{gb,i}}$  & 2.401086e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         ${k_{gb,v}}$  & 2.400580e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         \hline
      \end{tabular}
    \end{table}
    \newpage
    Sink strength plots are presented in Fig. \ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}. The effect of flipping behavior is not visible in grain boundary sink strength, ${Z^{gb}}$ plot, but in total grain boundary sink strength, ${k^2}$ plot, there is a significant change on ${k^2_i}$ after critical grain size of ${\sim}$1000 nm. In high dose rate plot, the critical grain size is seen clearly around at ${\sim}$250 nm.
      % \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
      %   \centering
      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_k}}
      %   \qquad
      %   \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_0_Z}}
      %   \caption{Sink Strengths for low dose rate neutron irradiation with 0\% Production Bias}
      %   \label{figure:sink_strengths_neutron_0_1e-6}
      % \end{figure}
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
        \caption{Sink Strengths for low dose rate neutron irradation with 5\% Production Bias}
        \label{figure:sink_strengths_neutron_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
        \caption{Sink Strengths for high dose rate neutron irradation with 5\% Production Bias}
        \label{figure:sink_strengths_neutron_5_1e-3}
      \end{figure}
  \newpage
  \subsection{Ion Irradiation} \hspace{10pt}
  Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic. Furthermore, they cannot penetrate through material too much because of their high energy loss in collisions. These characteristic causes a non-uniform defect production profile. The defect production profile used for ion irradation simulations are shown in Fig. \ref{figure:defect_production}. The dose rate, K\textsubscript{0} and domain size (1000 nm) would be scaled for different cases, but the profile is going to stay unchanged.
    \begin{figure}[h!]  %Ion irradation
      \centering
      \subfloat{\includegraphics[scale=0.27]{defect_production}}
      \qquad
      \caption{Defect production profile for ion irradation.}
      \label{figure:defect_production}
    \end{figure}
    \subsubsection{Concentrations} \hspace{10pt}
    The effect of defect production distribution is the first thing that can be observed easily on concentration profiles. Since, all defect production profiles having peak at around half of the domain, the concentration profiles are also showing the same behavior and reaching maximum at the center of domain, then waning through boundaries.

    If production bias is zero, maximum concentration that point defects can reach is equal for all different domain sizes shown in Fig. \ref{figure:concentrations_ion_0_1e-6}. High ion dose rate is scaling up the concentration levels without making a significant change in profiles (see Fig. \ref{figure:concentrations_ion_0_1e-3}).
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
        \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
        \caption{Concentration profiles for high dose rate ion irradiation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-3}
      \end{figure}
      \newpage
      In case of applying production bias, profiles become completely different. Although the flipping behavior observed in neutron irradation case is also visible in ion irradation case, the non-uniform defect production causes asymmetrical interstitial concentration profile in Fig. \ref{figure:concentrations_ion_5_1e-6}. The vacancy concentration profiles also become asymmetrical and shift up with increasing domain size. Increasing ion dose rate from 1e-6 dpa/s to 1e-3 dpa/s reduces the effect of defect production profile as well as critical grain size to flip (see Fig. \ref{figure:concentrations_ion_5_1e-3}).
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
        \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
        \caption{Concentration profiles for high dose rate ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-3}
      \end{figure}

>>>>

    \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
      \centering
      \subfloat{\includegraphics[scale=0.55]{average_concentration_neutron_5_size}}
      \qquad
      \subfloat{\includegraphics[scale=0.55]{average_concentration_high_neutron_5_size}}
      \caption{Average Concentration profiles for low and high dose neutron irradation with 5\% Production Bias}
      \label{figure:average_concentrations_neutron_5}
    \end{figure}

@@

  The results of bencmark problem, previously discussed in Fig. \ref{figure:concentrations_MOOSE_analytical}, can also be used to validate MOOSE sink strength calculations. Table \ref{table:sink_strengths_calculations} show the comparison of calculations.
    \begin{table}[h!]
      \centering
      \caption{Comparison of sink strength calculations}
      \label{table:sink_strengths_calculations}
      \begin{tabular}{ ||p{2cm}|p{3cm}|p{3cm}||  }
         \hline
          & MOOSE & Analytical\\
         \hline\hline\hline
         ${Z_{gb,i}}$  & 1.257206e-05 m & 1.257332e-05 m\\
         ${Z_{gb,v}}$  & 1.256941e-05 m & 1.257332e-05 m\\
         ${k_{gb,i}}$  & 2.401086e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         ${k_{gb,v}}$  & 2.400580e+13 m^{-2} & 2.401327e+13 m^{-2}\\
         \hline
      \end{tabular}
    \end{table}
    \newpage
    Sink strength plots are presented in Fig. \ref{figure:sink_strengths_neutron_5_1e-6} and \ref{figure:sink_strengths_neutron_5_1e-3}. The effect of flipping behavior is not visible in grain boundary sink strength, ${Z^{gb}}$ plot, but in total grain boundary sink strength, ${k^2}$ plot, there is a significant change on ${k^2_i}$ after critical grain size of ${\sim}$1000 nm. In high dose rate plot, the critical grain size is seen clearly around at ${\sim}$250 nm.
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_Z_scaled}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_5_k_scaled}}
        \caption{Sink Strengths for low dose rate neutron irradation with 5\% Production Bias}
        \label{figure:sink_strengths_neutron_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_Z_scaled}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_high_neutron_5_k_scaled}}
        \caption{Sink Strengths for high dose rate neutron irradation with 5\% Production Bias}
        \label{figure:sink_strengths_neutron_5_1e-3}
      \end{figure}
      \begin{figure}[h!]  %GB Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zi_scaled}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{sink_strength_Zv_scaled}}
        \caption{GB Sink Strengths for low dose rate neutron irradation}
        \label{figure:sink_strengths_neutron_bias_Z}
      \end{figure}
      \begin{figure}[h!]  %Total GB Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_ki_scaled}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{sink_strength_kv_scaled}}
        \caption{Total GB Sink Strengths for high dose rate neutron irradation}
        \label{figure:sink_strengths_neutron_bias_k}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s
        \centering
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_Z_scaled}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{sink_strength_moose_neutron_3D_k_scaled}}
        \caption{Sink Strengths for low dose rate neutron irradiation}
        \label{figure:sink_strength_moose_neutron_3D}
      \end{figure}
  \newpage
  \subsection{Ion Irradiation} \hspace{10pt}
  Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic. Furthermore, they cannot penetrate through material too much because of their high energy loss in collisions. These characteristic causes a non-uniform defect production profile. The defect production profile used for ion irradation simulations are shown in Fig. \ref{figure:defect_production}. The dose rate, K\textsubscript{0} and domain size (1000 nm) would be scaled for different cases, but the profile is going to stay unchanged.
    \begin{figure}[h!]  %Ion irradation
      \centering
      \subfloat{\includegraphics[scale=0.27]{defect_production}}
      \qquad
      \caption{Defect production profile for ion irradation.}
      \label{figure:defect_production}
    \end{figure}
    \subsubsection{Concentrations} \hspace{10pt}
    The effect of defect production distribution is the first thing that can be observed easily on concentration profiles. Since, all defect production profiles having peak at around half of the domain, the concentration profiles are also showing the same behavior and reaching maximum at the center of domain, then waning through boundaries.

    If production bias is zero, maximum concentration that point defects can reach is equal for all different domain sizes shown in Fig. \ref{figure:concentrations_ion_0_1e-6}. High ion dose rate is scaling up the concentration levels without making a significant change in profiles (see Fig. \ref{figure:concentrations_ion_0_1e-3}).
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-0}}
        \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-0}}
        \caption{Concentration profiles for high dose rate ion irradiation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-3}
      \end{figure}
      \newpage
      In case of applying production bias, profiles become completely different. Although the flipping behavior observed in neutron irradation case is also visible in ion irradation case, the non-uniform defect production causes asymmetrical interstitial concentration profile in Fig. \ref{figure:concentrations_ion_5_1e-6}. The vacancy concentration profiles also become asymmetrical and shift up with increasing domain size. Increasing ion dose rate from 1e-6 dpa/s to 1e-3 dpa/s reduces the effect of defect production profile as well as critical grain size to flip (see Fig. \ref{figure:concentrations_ion_5_1e-3}).
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-low_ion-5}}
        \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{interstitial_concentration_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{vacancy_concentration_500-5000nm-ion-5}}
        \caption{Concentration profiles for high dose rate ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Neutron - average conc - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.55]{average_concentration_ion_5_size}}
        \qquad
        \subfloat{\includegraphics[scale=0.55]{average_concentration_low_ion_5_size}}
        \caption{Average Concentration profiles for low and high dose ion irradation with 5\% Production Bias}
        \label{figure:average_concentrations_neutron_5}
      \end{figure}
